Interactively Visualizing Multivariate Market Segmentation Using the R Package Lionfish

### 2024-10-02 manuscript.tex
changed the capitalisation of the plot indices of the intro plots to be uniform with the rest of the figures. More making of programming languages and packages

\begin{figure*}[ht]
\centerline{\includegraphics[width=1\textwidth]{images/intro1.png}}
\caption{Examples of how $k$-means partitions 2D data with different association structure. If the correlation is high (c), the partitioning happens along the primary direction of the association.}
\label{kmeans-partition}
\end{figure*}

\begin{figure*}[ht]
\centerline{\includegraphics[width=1\textwidth]{images/intro2.png}}
\caption{The four $k$-means partitions plotted as histograms of the individual features. While differences between groups can be seen, the clear separation cannot. This is important for understanding why high-dimensional visualisation methods are useful for summarising partitioning results.}
\label{kmeans-histogram}
\end{figure*}

@@

While tour animations are best obtained within \proglang{R} using the tourr package~\citep{tourr}, it does not enable the interactivity required for example for a manual tour~\citep{laa2023new}. Interactive graphics are available when using Javascript, as implemented in the detourr package \citep{RJ-2023-052}. This allows to replay a recorded tour path with interactive graphics, and can also be linked with additional displays, but lacks capabilities for manual tours.

To integrate user interactions with the capabilities of the tourr package an active communication with the interface is required. For example, we may wish to explore the local neighbourhood of a projection selected by the user with a local tour animation provided by tourr, or we may want to optimize a guided tour path using groups identified via brushing.
Our solution is using \proglang{Python} for high-performance interactivity, through the packages \texttt{TKinter} \citep{lundh1999introduction}, \texttt{CustomTKinter} \citep{schimansky24}, and \texttt{matplotlib} \citep{Hunter:2007}, with integration to the tourr package \citep{tourr} via \texttt{reticulate} \citep{reticulate}, a framework that facilitates seamless interoperability between \proglang{Python} and \proglang{R}.

@@

We can further explore the similarities between the clusters by initializing an \texttt{interactive\_tour()} with a 2D tour based on the linear discriminant analysis (LDA) projection pursuit index. By navigating through the tour, we can observe various projections, and when a projection that separates the clusters is found, we highlight each cluster sequentially. The different highlighted clusters can be seen in Figure \ref{fig:silhouette_comparison}.

>>>>

\begin{figure*}[ht]
\centerline{\includegraphics[width=1\textwidth]{images/intro1.pdf}}
\caption{Examples of how $k$-means partitions 2D data with different association structure. If the correlation is high (C), the partitioning happens along the primary direction of the association.}
\label{kmeans-partition}
\end{figure*}

\begin{figure*}[ht]
\centerline{\includegraphics[width=1\textwidth]{images/intro2.pdf}}
\caption{The four $k$-means partitions plotted as histograms of the individual features. While differences between groups can be seen, the clear separation cannot. This is important for understanding why high-dimensional visualisation methods are useful for summarising partitioning results.}
\label{kmeans-histogram}
\end{figure*}

@@

While tour animations are best obtained within \proglang{R} using the tourr package~\citep{tourr}, it does not enable the interactivity required for example for a manual tour~\citep{laa2023new}. Interactive graphics are available when using \proglang{Javascript}, as implemented in the \texttt{detourr} package \citep{RJ-2023-052}. This allows to replay a recorded tour path with interactive graphics, and can also be linked with additional displays, but lacks capabilities for manual tours.

To integrate user interactions with the capabilities of the \texttt{tourr package} an active communication with the interface is required. For example, we may wish to explore the local neighbourhood of a projection selected by the user with a local tour animation provided by tourr, or we may want to optimize a guided tour path using groups identified via brushing.
Our solution is using \proglang{Python} for high-performance interactivity, through the packages \texttt{TKinter} \citep{lundh1999introduction}, \texttt{CustomTKinter} \citep{schimansky24}, and \texttt{matplotlib} \citep{Hunter:2007}, with integration to the tourr package \citep{tourr} via \texttt{reticulate} \citep{reticulate}, a framework that facilitates seamless interoperability between \proglang{Python} and \proglang{R}.

@@

We can further explore the similarities between the clusters by initializing an \texttt{interactive\_tour()} with a 2D tour based on the LDA projection pursuit index. By navigating through the tour, we can observe various projections, and when a projection that separates the clusters is found, we highlight each cluster sequentially. The different highlighted clusters can be seen in Figure \ref{fig:silhouette_comparison}.
